### 2023-06-30 1.Introduction/1.motivation.tex
Changed paths in main doc
Worked on motivation

Nowadays, it's impossible not to have heard about \acp{AI}, they are everywhere and everybody talks about them. The most recent example being \textit{ChatGPT} from \textbf{OpenAI} and is getting very popular even outside of the "computer community"(TODO : Find better term). Everybody is using those tools. It's clear that \ac{AI} is becoming more and more important in the current world.

@@

\begin{figure}[h!]
    \centering
    \includesvg[height=8cm]{Figures/Colored_neural_network.svg}
    \caption{Simple \acl{NN}}
    \label{fig:snn}
\end{figure}

@@

\begin{figure}[h!]
    \centering
    \includesvg[height=8cm]{Figures/NN_explained.svg}
    \caption{\aclp{NN} with names}
    \label{fig:nn_explained}
\end{figure}

>>>>

Nowadays, it's impossible not to have heard about \acp{AI}, they are everywhere and everybody talks about them. The most recent example being \textit{ChatGPT} from \textbf{OpenAI} and is getting very popular even among casual computer users. Everybody is using those tools. It's clear that \ac{AI} is becoming more and more important in the current world.

\acp{AI} are very power hungry algorithms which limits its use in embedded systems and power efficient devices.
Furthermore, the time an \ac{AI} takes to compute its output can become quite long. So much so that the most complex ones only run on online and very powerful servers, like the aforementioned \textit{ChatGPT}.

There are several options to reduce execution speed and energy consumption such as running the algorithm on a \ac{GPU} rather than a \ac{CPU}. Using an \ac{FPGA} or \ac{ASIC} are other ways to improve power consumption and execution time.
The latter is the most restricting (as it's name implies) but has the best results.

Using an \ac{ASIC} allows the use of analog computation. Analog computation offers great advantages compared to digital computers as it's much faster while being very power-efficient.

% For the State of the art

@@

\begin{figure}[h!]
  \centering
  \includesvg[height=8cm]{Colored_neural_network.svg}
  \caption{Simple \acl{NN}}
  \label{fig:snn}
\end{figure}

@@

\begin{figure}[h!]
  \centering
  \includesvg[height=8cm]{NN_explained.svg}
  \caption{\aclp{NN} with names}
  \label{fig:nn_explained}
\end{figure}
